How Tree-like are the data?

### 2019-04-11 phylotreelike.rmd
syncing

```{r crazy tree, echo=FALSE, message=FALSE}
library(ape)
library(ggplot2)
library(dplyr)
library(tidyr)

@@

>>>>

```{r crazy tree, echo=FALSE, message=FALSE}
library(ape)
library(ggplot2)
library(dplyr)
library(tidyr)
library(mvtnorm)

@@

## Likelihood surface

```{r likelihood surface, warning=FALSE, echo=FALSE, message=FALSE}

pp <- expand.grid(t1 = seq(-10,10,length=31)
  , t2 = seq(-10,10,length=31)    ## non-focal parameter
  , t3 = seq(-3,3,length=9)
)

ll <- sapply(1:nrow(pp),function(x){mvtnorm::dmvnorm(pp[x,1:3], mean =c(0,0,0), sigma = Vphy, log = TRUE)})

pp$ll <- ll
gg0 <- (ggplot(pp,aes(t1,t2))
    + facet_wrap(~t3,labeller=label_both)
    + geom_raster()
    + scale_fill_viridis_c()
#     + scale_x_continuous(expand=c(0,0))
#     + scale_y_continuous(expand=c(0,0))
    + theme(panel.spacing=grid::unit(0,"lines"))
)

gg0L <- gg0+ geom_raster(aes(fill=ll))

print(gg0L)

squash <- function(vals, matchvals) {
    sapply(vals,function(x) matchvals[which.min(abs(x-matchvals))])
}

dd_squash <- dd
dd_squash$t3 <- squash(dd$t3,unique(pp$t3))
samp_dd <- head(dd_squash,1000)
samp_dd$ll <- sapply(1:nrow(samp_dd),function(x){mvtnorm::dmvnorm(samp_dd[x,1:3], mean =c(0,0,0), sigma = Vphy, log = TRUE)})

print(gg0L 
  + geom_point(data=samp_dd, aes(x=t1, y=t2),size=0.1)
  + xlim(c(-10,10))
  + ylim(c(-10,10))
)
```
